### 2023-10-11 4.Results/airline.tex
Going to lunch
Few more lines

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    %\rowcolor{gray}
    \cellcolor[HTML]{808080}\acs{RMSE} & Original data & Digital output & Custom activation functions\\
    \hline
    Original data &\cellcolor[HTML]{202020} & $45.24$ & $45.94$\\
    \hline
    Digital output & $45.24$ & \cellcolor[HTML]{202020} & $4.04$\\
    \hline
    Custom activation function & $45.94$ & $4.04$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\ac{RMSE} errors of each curve to the others}
  \label{tab:airlineDigital}
\end{table}

@@

Those two

>>>>

\begin{table}[H]
  \centering
  \begin{tabular}{|c|c|c|c|}
    \hline
    %\rowcolor{gray}
    \cellcolor[HTML]{808080}\acs{RMSE} & Original data & Classic prediction & Custom activation functions\\
    \hline
    Original data &\cellcolor[HTML]{202020} & $45.24$ & $45.94$\\
    \hline
    Digital output & $45.24$ & \cellcolor[HTML]{202020} & $4.04$\\
    \hline
    Custom activation function & $45.94$ & $4.04$ & \cellcolor[HTML]{202020}\\
    \hline
  \end{tabular}
  \caption{\ac{RMSE} errors of each curve to the others}
  \label{tab:airlineDigital}
\end{table}

@@

Those two curves are both very close to the target curve. They have a very similar error rate to this target curve, indeed they're \ac{RMSE} error is $45.24$ for the training using the original activation functions, and $45.94$ for the data created with the analog activation function. The difference of error between the two prediction is of about seven hundred passengers, which is very low considering the scale.

Computing the \ac{NN} with or without the analog activation functions doesn't affect the digital prediction of the \ac{NN}. An error difference so low can be due to the initial weights of the \ac{NN}, before it was trained. Furthermore, training the \ac{NN} for a few more epochs would change the errors by enough to make this difference negligible.
